Possible Exoskeleton Control Architectures and Algorithms\\ (Draft 4.0)

### 2015-09-30 control.tex
more updates

\title{A Survey of Possible Exoskeleton Control Architectures and
Algorithms\\
(Draft 3.1)}

@@

\begin{abstract}
Abstract to be written.
\end{abstract}

@@

Executive Summary to be written.

@@

This paper surveys possible exoskeleton control architectures and
algorithms.
One goal is to address the question:
{\it How do exoskeleton control approaches compare with 
approaches to humanoid robot control?}
A companion paper surveys implemented exoskeleton control architectures
and algorithms [survey.pdf].

@@

If you ask people who research complex computationally expensive
high end control
systems for a living how to control a system,
they will recommend complex computationally expensive high end control systems.
It is entirely possible that simple local low dimensional controllers
designed using traditional (frequency domain) techniques will do
quite well, especially if the appropriate sensors (such as 
operator-exoskeleton force sensors) are available.

@@

Same for constraint enforcement (such as avoiding self-collisions)
in either optimization or feedback control (barrier
Lyapunov functions (BLF)~\cite{IEEE06911561}).

@@

We recommend the following hierarchical control architecture~\cite{IEEE06907051}:

@@

Low level control presents an API (Application Programmer Interface)
for higher control levels
to access the actuators, sensors, and other robot hardware~\cite{IEEE07271219}.
It implements high servo rate processing including feedback control and online
optimization.
This level provides an idealization of the exoskeleton in two ways: 
{\it What degrees of freedom (DOF) are controlled?,} and 
{\it How is a degree of freedom controlled?}

>>>>

\title{Possible Exoskeleton Control Architectures and Algorithms\\
(Draft 4.0)}

@@

@@

We recommend a red team that explores frequency domain control system
design, as well as an emphasis on ``modern'' control in this paper.

\section{Clickable web links}

The web links (URLs) below can be clicked on to view, if your PDF viewer/browser supports that. On our browsers you actually have to click on the black
part of a letter, not just in the blue box (if present).

@@

This paper surveys possible exoskeleton control architectures and
algorithms.
One goal is to address the question:
{\it How do exoskeleton control approaches compare with 
approaches to humanoid robot control?}
A companion paper surveys implemented exoskeleton control architectures
and algorithms.\\
\url{http://www.cs.cmu.edu/~cga/exo/survey.pdf}

@@

If you ask people who research complex computationally expensive
high end control
systems for a living how to control a system,
they will recommend complex computationally expensive high end control systems.
It is entirely possible that simple local low dimensional controllers
designed using traditional (frequency domain) techniques will do
quite well, especially if the appropriate sensors (such as 
operator-exoskeleton force sensors) are available.
It may even be the case that frequency domain techniques will handle
structural modeling error (jello-like human operators, deformable materials
(straps and pads, wires and hoses), and structural deformation and joint
play in lightweight frames) better than the state space oriented techniques
advocated here.

We recommend a red team that explores frequency domain control system
design, as well as an emphasis on ``modern'' control here.

@@

Same for constraint enforcement (such as avoiding self-collisions)
in either optimization or feedback control (barrier
Lyapunov functions (BLF).\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=6911561}

@@

We recommend the following hierarchical control architecture.
% review? \url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=6907051}

@@

Low level control presents an API (Application Programmer Interface)
for higher control levels
to access the actuators, sensors, and other robot hardware.\\
\url{http://ieeexplore.ieee.org/xpl/login.jsp?tp=&arnumber=7271219}\\
It implements high servo rate processing including feedback control and online
optimization.
This level provides an idealization of the exoskeleton in two ways: 
{\it What degrees of freedom (DOF) are controlled?,} and 
{\it How is a degree of freedom controlled?}
